Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-16 report/report.tex
Fix reference author formatting
Convert non-scientific references to footnotes

The SLU map is maintained by The Swedish National Land Survey (Swedish: Lantmäteriet).
The data is collected by geodetic professionals, by land surveying methods such as GPS or DGNSS positioning, or by reproduction of features from ortophoto or stereo mapping from 3D aerial images.
Building features in the SLU dataset have a position accuracy requirement of 2 meters.
The SLU map contains building features and property limits, but no road data.
The map is updated continously by Lantmäteriet, in conjoncture with the forming or reforming of property.
Whereas OSM is a free service, the SLU map is available to paying customers or for free to students and researchers.
(Lantmäteriet, 2019)

@@

The SLU dataset is delivered in the SWEREF 99 TM coordinate system (Lantmäteriet, 2019). SWEREF 99 TM is a projected coordinate system and there is no linear transformation to the WGS 48 system, which OSM uses (OSM 19). The coordinate conversions for this paper were obtained using proj: a Linux commandline application for geospatial coordinate conversion.

@@

Let us briefly go over all of van Oorts accuracy criteria that will not be assessed through this study.
Let us see how they could be obtained and assessed for both the OSM and SLU maps, staring with the data lineage.
The lineage aspect of the OSM data is available through the OSM History Viewer, an online debugging tool that lets anyone freely view the change history of individual fetures in a commit history-like fashion.
There is an option for editors to include a personal note with their changesets to include additional details or motivate why a change was made, but there is no guaratee that the data includes any information on the aquisition method used (OSM 2020).
The history aspect of the SLU dataset is not freely available online, but the acquistion method is included in the file metadata on a per-object basis.
Lantmäteriet uses internal codes to specifify the acquistion method, and these codes can be referred to in the product description the accompanies the map files.
As the scope of this project is limited to making a broad comparison of the positional accuracy of the two datasets, only the required positional accuracy as described by the SLU product description will be used.

@@

The default minimum widths were obtained from (Trafikverket, 20). The standard recommended minimum width for a two-lane road in Sweden is 6.5 meters.
Subsequent visual measurements of a few key locations in the Stockholm area revealed the following minimum way widths:
Table \ref{table:road-widths} shows the minimum and maximum road widths that were found during these measurements, and that will be used in the collision study.

@@

\bibitem{douglas-73}
Douglas, D.H. \& Peucker T.K. (1973). Algorithms for the Reduction of the Number of Points Required to Represent a Digitalized Line or Its Caricature. Cartographica: The International Journal for Geographic Information and Geovisualization, 10(2), 112-122.

\bibitem{fan-14}
Fan, Hongchao \& Zipf, Alexander \& Fu, Qing \& Neis, Pascal. (2014). Quality assessment for building footprints data on OpenStreetMap. International Journal of Geographical Information Science. 28. 700-719.

@@

\bibitem{lantmateriet-19}
Lantmäteriet. (2019). Produktbeskrivning: GSD-Fastighetskartan vektor. Acessed 16-04-2020.
https://www.lantmateriet.se/globalassets/kartor-och-geografisk-information/kartor/fastshmi.pdf.

\bibitem{osm-19}
OSM. (2019). Converting to WGS84 - OpenStreetMap Wiki. Accessed 13-03-2020.
https://wiki.openstreetmap.org/wiki/Converting\_to\_WGS84.

\bibitem{osm-20}
OSM. (2020). OSM History Viewer - OpenStreetMap Wiki. Accessed 20-03-2020
https://wiki.openstreetmap.org/wiki/OSM\_History\_Viewer.

@@

\bibitem{trafikverket-20}
Trafikverket. (2020). Vägars och gators utformning. Publikation 2020:029. \\
https://trafikverket.ineko.se/Files/sv-SE/71830/ \\
Ineko.Product.RelatedFiles/2020\_029\_vagar\_och\_gators\_utformning\_krav.pdf

>>>>

The SLU map is maintained by The Swedish National Land Survey (Swedish: Lantmäteriet).
The data is collected by geodetic professionals, by land surveying methods such as GPS or DGNSS positioning, or by reproduction of features from ortophoto or stereo mapping from 3D aerial images.
Building features in the SLU dataset have a position accuracy requirement of 2 meters.
The SLU map contains building features and property limits, but no road data.
The map is updated continously by Lantmäteriet, in conjoncture with the forming or reforming of property.
Whereas OSM is a free service, the SLU map is available to paying customers or for free to students and researchers. \footnote{Lantmäteriet. Produktbeskrivning: GSD-Fastighetskartan vektor - Lantmäteriet. Acessed 16-04-2020. https://www.lantmateriet.se/globalassets/kartor-och-geografisk-information/kartor/fastshmi.pdf}

@@

The SLU dataset is delivered in the SWEREF 99 TM coordinate system.
SWEREF 99 TM is a projected coordinate system and there is no linear transformation to the WGS 48 system, which OSM uses. \footnote{Converting to WGS84 - OpenStreetMap Wiki. Accessed 13-03-2020. https://wiki.openstreetmap.org/wiki/Converting\_to\_WGS84}
The coordinate conversions for this paper were obtained using proj: a Linux commandline application for geospatial coordinate conversion.

@@

Let us briefly go over all of van Oorts accuracy criteria that will not be assessed through this study.
Let us see how they could be obtained and assessed for both the OSM and SLU maps, staring with the data lineage.
The lineage aspect of the OSM data is available through the OSM History Viewer, an online debugging tool that lets anyone freely view the change history of individual fetures in a commit history-like fashion.
There is an option for editors to include a personal note with their changesets to include additional details or motivate why a change was made, but there is no guaratee that the data includes any information on the aquisition method used \footnote{OSM History Viewer - OpenStreetMap Wiki. Accessed 20-03-2020. https://wiki.openstreetmap.org/wiki/OSM\_History\_Viewer}
The history aspect of the SLU dataset is not freely available online, but the acquistion method is included in the file metadata on a per-object basis.
Lantmäteriet uses internal codes to specifify the acquistion method, and these codes can be referred to in the product description the accompanies the map files.
As the scope of this project is limited to making a broad comparison of the positional accuracy of the two datasets, only the required positional accuracy as described by the SLU product description will be used.

@@

See the footnote for the publication that the default minimum widths were obtained from. \footnote{Vägars och gators utformning - Trafikverket. Publikation 2020:029. https://trafikverket.ineko.se/Files/sv-SE/71830/\\Ineko.Product.RelatedFiles/2020\_029\_vagar\_och\_gators\_utformning\_krav.pdf}
The standard recommended minimum width for a two-lane road in Sweden is 6.5 meters.

Subsequent visual measurements of a few key locations in the Stockholm area revealed the following minimum way widths:
Table \ref{table:road-widths} shows the minimum and maximum road widths that were found during these measurements, and that will be used in the collision study.

@@

\bibitem{douglas-73}
Douglas, D.H. and Peucker T.K. (1973). Algorithms for the Reduction of the Number of Points Required to Represent a Digitalized Line or Its Caricature. Cartographica: The International Journal for Geographic Information and Geovisualization, 10(2), 112-122.

\bibitem{fan-14}
Fan, H., Zipf, A., Fu, Q. and Neis, P. (2014). Quality assessment for building footprints data on OpenStreetMap. International Journal of Geographical Information Science. 28. 700-719.

@@

@@
